{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-28 bmvc_review.tex
Revised the introduction.

%%%%%%%%% BODY TEXT
\section{Introduction}
\begin{comment}
\begin{itemize}
\item YoungWoo: Clean up the introduction
\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
\item By Monday, we'll have a draft ready to submit.
\end{itemize}
\end{comment}
A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry other
sensors than a lightweight or an array of monocular cameras. For
example, instead of having just bare flight function with video
recording, an unmanned air vehicle (UAV) equipped with object or
feature following would make it more useful in the application of
monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking that aims at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
400Hz so that it could run up to 40Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online object tracking is more
appropriate.

>>>>

%%%%%%%%% BODY TEXT
\section{Introduction}
\begin{comment}
\begin{itemize}
\item YoungWoo: Clean up the introduction
\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
\item By Monday, we'll have a draft ready to submit.
\end{itemize}
\end{comment}
A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deploying intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a lightweight or an array of monocular cameras. For
example, instead of having just bare flight function with video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking aiming at running
on any embedded or mobile platforms that doesn't require an offline
training, and can run on an embedded system. In particular, we would
like to make our algorithm 1) learn the appearance model of a target
on the fly and 2) run as fast on a typical desktop as up to 300Hz so
that it could run, at least, faster than 30Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online object tracking is more
appropriate.
